Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2014-10-25 tex/scam/sparsistency.tex

We divide our analysis into two parts. We first establish a sufficient
deterministic condition that $\hat{S} = S$ and we then consider the
stochastic setting and argue that the deterministic conditions hold
with high probability. Note that in all of our results and analysis, we let $c,
C$ represent absolute constants; the actual values of $c,C$ may change from line to line. We derived two equivalent optimizations for AC/DC: \eqref{np} outputs $\hat{f}_k, \hat{g}_k$ and \eqref{opt:alternate_opt} outputs the second derivatives $\hat{d}_k$. Their equivalence is established in Proposition~\ref{prop:alt_opt_form} and we use both $\hat{d}_k$ and $\hat{f}_k$ in our analysis without further stating their relationships.

>>>>

We divide our analysis into two parts. We first establish a sufficient
deterministic condition for consistency of the sparsity pattern
screening procedure.  We then consider the stochastic setting and argue that the 
deterministic conditions hold with high probability. Note that in all of our results 
and analysis, we let $c,
C$ represent absolute constants; the actual values of $c,C$ may change from line to line. We derived two equivalent optimizations for AC/DC: \eqref{np} outputs $\hat{f}_k, \hat{g}_k$ and \eqref{opt:alternate_opt} outputs the second derivatives $\hat{d}_k$. Their equivalence is established in Proposition~\ref{prop:alt_opt_form} and we use both $\hat{d}_k$ and $\hat{f}_k$ in our analysis without further stating their relationships.
